Synthesizing Symmetric Lenses

### 2018-06-30 papers/SymmetricLenses/main.tex
add example of entropy calcs

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage[inline]{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}

@@

\saz{The following is hard to follow} Eventually, we cut the proposal-synthesis
loop short. Before proposing new types \RXSearch evaluates whether it should
continue proposing regular expression pairs, or whether it is content with lens
of lowest cost seen thus far. If there are a large number of regular expression
pairs that are equally dissimilar to the originals or if the current lens is
very well synchronized, \RXSearch stops. By doing this \RXSearch continues
searching for better lenses, but does not tackle huge search spaces unless it
needs to. In this way, the algorithm can provide lenses quickly to the users,
which users can refine with additional examples.
% end overview

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage[inline]{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{letltxmacro}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}

@@

\saz{The following is hard to follow} Eventually, we cut the proposal-synthesis
loop short. Before proposing new types \RXSearch evaluates whether it should
continue proposing regular expression pairs, or whether it is content with lens
of lowest cost seen thus far. If there are a large number of regular expression
pairs that are equally dissimilar to the originals or if the current lens is
very well synchronized, \RXSearch stops. By doing this \RXSearch continues
searching for better lenses, but does not tackle huge search spaces unless it
needs to. In this way, the algorithm can provide lenses quickly to the users,
which users can refine with additional examples.

\afm{calculations for cost of various lenses between \lstinline{emp_salary} and
  \lstinline{emp_row}} Consider the lens \lstinline{single_emp_map} between
\lstinline{emp_salary} and \lstinline{emp_row}. Given this lens, the expected
entropy of recovering the left format from the right
($\EntropyOf{\lstinline{emp_salary} \Given \lstinline{emp_row},
  \lstinline{single_emp_map} }$) is the sum of the expected entropy of
recovering each of its subcomponents, $\EntropyOf{\lstinline{emp_salary} \Given
  \lstinline{emp_row}, \lstinline{single_emp_map} } = \EntropyOf{\lstinline{name
    . " " . name} \Given \lstinline{name . "," . name}, \lstinline{name_map}
}$\\ + $\EntropyOf{\lstinline{": " . salary} \Given
  \lstinline{"," . company}, \lstinline{disc(salary,company,"UNSET","UNSET")}
}$.

The entropy of the identity lens is zero. As the two formats are in bijective
correspondence, we know exactly which string is present in the left-hand format.
The entropy of the disconnect lens is just the entropy of
\lstinline{": " . salary}.  Knowing which string is present in the right-hand
format tells us nothing about what string is present in the left-hand format. So
$\EntropyOf{\lstinline{emp_salary} \Given \lstinline{emp_row},
  \lstinline{single_emp_map} } = \EntropyOf{\lstinline{": " . salary} }$

Analogously, $\EntropyOf{\lstinline{emp_row} \Given \lstinline{emp_salary},
  \lstinline{single_emp_map} }$ is just $\EntropyOf{\lstinline{"," . company}
}$, so the total cost of the lens is $\EntropyOf{\lstinline{": " . salary}} +
\EntropyOf{\lstinline{"," . company}}$

Consider the trivial lens
\lstinline{disc(emp_salary,emp_row,rep(emp_salary),rep(emp_row))}. As this is
the disconnect lens, the cost of each side is the entropy of the data format, so
the total cost is $\EntropyOf{\lstinline{emp_salary}} +
\EntropyOf{\lstinline{emp_row}}}$. \lstinline{emp_salary} contains strictly more
imformation than \EntropyOf{\lstinline{": " . salary}}, and \lstinline{emp_row}
contains strictly more information than \EntropyOf{\lstinline{": " . salary}},
so by our metric \lstinline{single_emp_map} is preferable to the disconnect
lens.
% end overview
